Relauo Amicus Brief Models

### 2022-05-16 modeling/justicemq-interactions/medauf.Rmd
add sgfem3 to interaction models

```{r}
mod3 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_abortion_regret + medauf_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_bad_law + medauf_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_evidence + medauf_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_fetus + medauf_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_final_authority + medauf_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_morality_religion + medauf_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_privacy + medauf_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_standing + medauf_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_undue_burden + medauf_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_womens_future_life + medauf_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_womens_health + medauf_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

>>>>

```{r}
mod3 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                medauf_abortion_regret + medauf_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                medauf_bad_law + medauf_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                medauf_evidence + medauf_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                medauf_fetus + medauf_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                medauf_final_authority + medauf_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                medauf_morality_religion + medauf_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                medauf_privacy + medauf_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                medauf_standing + medauf_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                medauf_undue_burden + medauf_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                medauf_womens_future_life + medauf_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                medauf_womens_health + medauf_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

### 2022-05-16 modeling/justicemq-interactions/medauo.Rmd
add sgfem3 to interaction models

---
title: "medauo Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

```{r}
mod3 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_abortion_regret + medauo_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_bad_law + medauo_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_evidence + medauo_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_fetus + medauo_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_final_authority + medauo_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_morality_religion + medauo_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_privacy + medauo_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_standing + medauo_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_undue_burden + medauo_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_womens_future_life + medauo_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_womens_health + medauo_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

>>>>

---
title: "Medauo Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

```{r}
mod3 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                medauo_abortion_regret + medauo_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                medauo_bad_law + medauo_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                medauo_evidence + medauo_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                medauo_fetus + medauo_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                medauo_final_authority + medauo_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                medauo_morality_religion + medauo_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                medauo_privacy + medauo_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                medauo_standing + medauo_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                medauo_undue_burden + medauo_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                medauo_womens_future_life + medauo_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                medauo_womens_health + medauo_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

### 2022-05-16 modeling/justicemq-interactions/relauf.Rmd
add sgfem3 to interaction models

```{r}
mod3 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_abortion_regret + relauf_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_bad_law + relauf_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_evidence + relauf_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_fetus + relauf_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_final_authority + relauf_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_morality_religion + relauf_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_privacy + relauf_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_standing + relauf_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_undue_burden + relauf_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_womens_future_life + relauf_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_womens_health + relauf_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

>>>>

```{r}
mod3 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                relauf_abortion_regret + relauf_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                relauf_bad_law + relauf_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                relauf_evidence + relauf_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                relauf_fetus + relauf_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                relauf_final_authority + relauf_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                relauf_morality_religion + relauf_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                relauf_privacy + relauf_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                relauf_standing + relauf_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                relauf_undue_burden + relauf_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                relauf_womens_future_life + relauf_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                relauf_womens_health + relauf_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

### 2022-05-16 modeling/justicemq-interactions/relauo.Rmd
add sgfem3 to interaction models

```{r}
mod3 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_abortion_regret + relauo_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_bad_law + relauo_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_evidence + relauo_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_fetus + relauo_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_final_authority + relauo_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_morality_religion + relauo_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_privacy + relauo_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_standing + relauo_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_undue_burden + relauo_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_womens_future_life + relauo_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_womens_health + relauo_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

>>>>

```{r}
mod3 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                relauo_abortion_regret + relauo_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                relauo_bad_law + relauo_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                relauo_evidence + relauo_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                relauo_fetus + relauo_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                relauo_final_authority + relauo_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                relauo_morality_religion + relauo_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                relauo_privacy + relauo_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                relauo_standing + relauo_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                relauo_undue_burden + relauo_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                relauo_womens_future_life + relauo_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                relauo_womens_health + relauo_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
